\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Paritosh Yadav}{
\href{mailto:prtshydv@gmail.com}{prtshydv@gmail.com} | \href{tel:+919896362525}{+91 9896362525}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.65\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Indiagold}
\descript{| Frontend Lead}
\location{Mar 2022 – Present | Abu Dhabi, UAE}
\hfill
\begin{tightemize}
\item Scalable Architecture \& Performance Optimization: Architected and refactored the Admin Dashboard, Web App improving stability to 99.999\%, reducing build time by 60\%, and optimizing performance for low-end devices.
\item SEO-Driven Marketing Website: Built a Next.js-based marketing website with Strapi CMS, driving organic traffic growth from 20-30 to 800k+ clicks/month and generating Rs. 40-50 lakhs/month in organic loan disbursals.
\item Team Leadership \& Productivity: Mentored a 7-member frontend team (now 3-members) while maintaining 2x productivity and delivering features faster.
\item A/B Testing \& Conversion Optimization: Developed an in-house A/B testing module, increasing ad conversion rates from 10-12\% to 28-30\%.
\item Tech Stack: ReactJs, NextJs, Strapi, GatsbyJs, Tailwind, Typescript
\end{tightemize}
\sectionsep

\runsubsection{StoryXpress}
\descript{| Full Stack Developer}
\location{Jan 2021 – Mar 2022 | Gurugram, India}
\begin{tightemize}
\item Cross-Platform Suite Development: Led a team of 3 to build StoryXpress Suite (Web, Desktop, Chrome Extension) for video recording, editing, and analytics, serving 1.5M users and 30M hours of content.
\item Performance Optimization: Reduced native app size by 40\% using Electron.js and improved web app performance, achieving 80+ Google Pagespeed score and passing Core Web Vitals.
\item SDK Development: Created SDKs for integration into LMS and HR systems, enhancing user engagement and satisfaction.
\item Tech Stack: ReactJs, Styled Components, ElectronJs, Web Socket, TypeScript
\end{tightemize}
\sectionsep

\runsubsection{Delinno}
\descript{| Full Stack Developer}
\location{Dec 2019 – Dec 2020 | Gurugram, India}
\begin{tightemize}
\item ESG Dashboard Development: Built a scalable ESG management dashboard using React, Styled Components, and Redux, enabling data-driven decision-making for clients.
\item Survey Platform: Contributed to a survey platform that completed 14,000+ surveys for global organizations and governments, using React (frontend) and Python (backend).
\item Learning Management System: Developed a fitness trainer LMS with 44K+ app downloads, leveraging Django (backend) and React + MUI (frontend).
\item Tech Stack: ReactJs, Django, MUI
\end{tightemize}
\sectionsep

\runsubsection{CSimplifyIT}
\descript{| Technical Consultant}
\location{Jan 2019 – Nov 2019 | Gurugram, India}
\begin{tightemize}
\item Google Add-ons Development: Created Simple Mass Mail Merge and Simple Recruitment Manager Google add-ons, streamlining email campaigns and recruitment processes.
\item OCR System: Built a Python-based OCR system using OpenCV, 30\% more efficient.
\item Tech Stack: OpenCv, Django, Google Apps Script, Apache Kaffka, Jquery
\end{tightemize}
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{TIT\&S}
\descript{B.Tech in Computer Science}
\location{Aug 2015 – Aug 2019 | Bhiwani, India}
\sectionsep

\subsection{Jain Public School}
\descript{XII in PCM}
\location{Apr 2014 – Apr 2015 | Rewari, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Frontend}
\textbullet{} React.js | Next.js | GatsbyJs \\ \textbullet{} JavaScript | TypeScript \\ \textbullet{} Redux | Zustand \\ \textbullet{} Web Sockets | Pusher \\ \textbullet{} CSS3 | Tailwind | Styled Components \\ \textbullet{} HTML5 | MUI \\ \textbullet{} VueJs | SolidJs (Personal Projects)
\sectionsep

\subsection{Backend \& DevOps}
\textbullet{} Node.js \\ \textbullet{} Python | Django \\ \textbullet{} AWS Amplify \\ \textbullet{} Vercel \\ \textbullet{} Strapi \\ \textbullet{} PostgreSQL | MySQL
\sectionsep

\subsection{Other}
\textbullet{} Prompt Engineering \\ \textbullet{} Google Tag Manager | Analytics | Search Console \\ \textbullet{} OpenCV \\ \textbullet{} Adobe Photoshop | After Effects 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
LinkedIn: \href{https://www.linkedin.com/in/parfectshot/}{View Profile} \\
GitHub: \href{https://github.com/parfectshot}{View Profile} \\
\sectionsep

\end{minipage}
\end{document}